\section*{References}

\begin{thebibliography}{99}
\bibitem{li2020fourier} Li, Z., Kovachki, N., Azizzadenesheli, K., Liu, B., Bhattacharya, K., Stuart, A., \& Anandkumar, A. (2020). Fourier neural operator for parametric partial differential equations. arXiv preprint arXiv:2010.08895.

\bibitem{raissi2019physics} Raissi, M., Perdikaris, P., \& Karniadakis, G. E. (2019). Physics-informed neural networks: A deep learning framework for solving forward and inverse problems involving nonlinear partial differential equations. Journal of Computational Physics, 378, 686-707.

\bibitem{hurst1951long} Hurst, H. E. (1951). Long-term storage capacity of reservoirs. Transactions of the American Society of Civil Engineers, 116(1), 770-799.

\bibitem{peng1994mosaic} Peng, C. K., Buldyrev, S. V., Havlin, S., Simons, M., Stanley, H. E., \& Goldberger, A. L. (1994). Mosaic organization of DNA nucleotides. Physical Review E, 49(2), 1685.

\bibitem{mandelbrot1968noah} Mandelbrot, B. B., \& Van Ness, J. W. (1968). Fractional Brownian motions, fractional noises and applications. SIAM Review, 10(4), 422-437.

\bibitem{abry1998wavelet} Abry, P., \& Veitch, D. (1998). Wavelet analysis of long-range-dependent traffic. IEEE Transactions on Information Theory, 44(1), 2-15.

\bibitem{veitch1999wavelet} Veitch, D., \& Abry, P. (1999). A wavelet-based joint estimator of the parameters of long-range dependence. IEEE Transactions on Information Theory, 45(3), 878-897.

\bibitem{robinson1995gaussian} Robinson, P. M. (1995). Gaussian semiparametric estimation of long range dependence. The Annals of Statistics, 23(5), 1630-1661.

\bibitem{geweke1984inference} Geweke, J., \& Porter-Hudak, S. (1984). The estimation and application of long memory time series models. Journal of Time Series Analysis, 4(4), 221-238.

\bibitem{whittle1951estimation} Whittle, P. (1951). Hypothesis testing in time series analysis. Almqvist \& Wiksells.

\bibitem{higuchi1988approach} Higuchi, T. (1988). Approach to an irregular time series on the basis of the fractal theory. Physica D: Nonlinear Phenomena, 31(2), 277-283.

\bibitem{kantelhardt2002multifractal} Kantelhardt, J. W., Zschiegner, S. A., Koscielny-Bunde, E., Havlin, S., Bunde, A., \& Stanley, H. E. (2002). Multifractal detrended fluctuation analysis of nonstationary time series. Physica A: Statistical Mechanics and its Applications, 316(1-4), 87-114.

% Add more references as needed
\end{thebibliography}
